### 2024-01-11 pnrs.tex
avancées

%! TeX program = xelatex
%! lang = en-GB
\documentclass[sigconf,natbib=false,screen, review,anonymous]{acmart}

@@

\begin{itemize}
    \item Use $\Nat$-polyregular functions all the time, and just 
        in the introduction talk about $\Nat$-rational series.
    \item Prove that $\Nat$-rational series of polynomial 
        growth are $\Nat$-polyregular functions, maybe using
        the results about ambiguity in automata?
        Theorem 5.22
    \item Define commutativity by a map 
        $\commute \colon \Sigma^* \to \Nat^{\Sigma}$.
    \item Define "commutative functions" and its symbol.
    \item Define "computed by" (like, recognised by) for commutative 
        functions.
    \item Change \cref{corrected-version:thm} to use directly
        star-free!
    \item Clear up the computability problems.
    \item Polynomial + Npolyregular => star free?
    \item Polynomial + N rational => N polyregular?
    \item cite the paper of Quantitative Monadic Second-Order Logic
        about why it is interesting class.
\end{itemize}

@@

\begin{fact}[{\cite[Exercise 1.2 p 169]{berstel2011noncommutative}}]
    \label{polynomial-rational-polyreg:fact}
    Let $\Sigma$ be a finite alphabet, and $f \colon \Sigma^* \to \Nat$
    be a function. The following are equivalent:
    \begin{enumerate}
        \item $f$ can be computed as a \k{$\Nat$-rational series}
            of \kl{polynomial growth}.
        \item $f$ is a \kl{$\Nat$-polyregular function}.
    \end{enumerate}
\end{fact}

\begin{definition}[Letter Counting Function]
    \label{commutative-map:def}
    Let $\Sigma$ be a finite alphabet. We define
    $\commute \colon \Sigma^* \to \Nat^\Sigma$ for the
    map that counts occurrences of every letter in the input word, namely:
    \begin{equation*}
        \commute[w] \defined \seqof{\card[a]{w}}{a \in \Sigma} \quad .
    \end{equation*}
\end{definition}

@@

    Assume by contradiction that $P$ is a \kl{$\Nat$-rational polynomial}.
    There exists a \kl{commutative}
    $\Nat$-rational series $f \colon \Sigma \to \Nat$
    such that $P(\card[a]{w}, \card[b]{w}, \card[c]{w}) = f(w)$.
    Remark that $P(X,Y,Z) = 0$
    if and only if $Z(X+Y)^2 = -2 (X-Y)^2$. Hence,
    $P(X,Y,Z)=0$ if and only if $Z = 0$ and $X = Y$, or 
    $Z \neq 0$, and $X = Y = 0$.

@@

\begin{definition}
    Let $\vec{X}$ be a finite tuple of indeterminate.
    The class $\CorrectPoly[\vec{X}]$ is the collection of
    polynomials $P \in \Rel[\vec{X}]$ such that
    $P$ is 
    such that, for every partial function $\nu \colon \vec{X} \to \Nat$,
    every \kl{maximal monomial} of
    $\restr{P}{\nu}$ has a \kl{positive coefficient}.
\end{definition}

@@

\begin{remark}
    \label{inductive-correct-poly:remark}
    Let $P \in \Rel[X,\vec{Y}]$ be a polynomial.
    The following are equivalent:
    \begin{enumerate}
        \item $P \in \CorrectPoly$,
        \item The \kl{maximal monomials} of 
            $P$ have \kl{positive coefficients},
            and 
            for all $n \in \Nat$,
            $\restr{P}{X = n} \in \CorrectPoly$.
    \end{enumerate}
    Furthermore, if $P \in \Rel[]$ is a polynomial without
    indeterminate, then $P \in \CorrectPoly$ if and only
    if its \kl{maximal monomial} (the constant term)
    has a \kl{positive coefficient}.
\end{remark}
\begin{proof}
    By induction on the number of indeterminate,
    leveraging the fact that if there exists at least one indeterminate
    $X$, i.e., that $\vec{X} = X \vec{Y}$, then for all $n \in \Nat$
    and partial function $\nu \colon \vec{Y} \to \Nat$,
    we have 
    \begin{equation*}
        \restr{\left(\restr{P}{X = n}\right)}{\nu} = \restr{P}{ \nu[X = n]}
        \quad
        ,
    \end{equation*}
    where $\nu[X = n]$ is the partial function from
    $\vec{X}$ to $\Nat$ that coincides with $\nu$ on $\vec{Y}$
    and maps $X$ to $n$.
\end{proof}

\begin{example}
    \label{n-poly-n-poly:example}
    Let $P \in \Nat[\vec{X}]$. Then, $P$
    is a \kl{$\Nat$-rational polynomial}.
\end{example}
\begin{proof}
    Let $P \in \Nat[\vec{X}]$, and $\nu \colon \vec{X} \to \Nat$
    be a partial function.
    Notice that $\restr{P}{\nu}$ continues to be
    a polynomial with \kl{positive coefficients}, and in particular
    with 
    \kl{maximal monomials} having \kl{positive coefficients}.
\end{proof}

@@

\begin{lemma}
    \label{n-poly-combinatorics:lem}
    Let $f$ be a  \kl{$\Nat$-polyregular} function. 
    There exists $\omega \in \Nat$
    such that for all $p \in \Nat$,
    for all $\alpha_0, \dots, \alpha_p \in \Sigma^*$,
    for all $u_1, \dots, u_p \in \Sigma^*$,
    there exists a polynomial $P \in \Rel[X_1, \dots, X_p]$
    whose \kl{maximal monomials} have \kl{positive coefficients},
    and such that:
    \begin{equation*}
        f(\alpha_0 \prod_{i = 1}^p (u_i^{\omega \times X_i} \alpha_i))
        = P(X_1, \dots, X_p) \quad .
    \end{equation*}
\end{lemma}
\begin{proof}[Proof Sketch]
    Let $\omega$ be an idempotent power for the finite monoid $M$.
    We define an equivalence between partitions of a word 
    $w \defined \alpha_0 \prod_{i = 1}^p (u_i^{\omega \times X_i} \alpha_i)$
    as follows: two partitions into $k$ words in $\Sigma^*$ are equivalent
    when normalizing them with the rules
    $u_i^{\omega} u_i^{\omega} \to u_i^{\omega}$ for all $1 \leq i \leq p$.
    This equivalence relation has finite index, and all partitions in the same
    equivalence class yield the same value through $\pi$, because
    $\mu(u_i^\omega) = \mu(u_i)^\omega$ is an idempotent element of the monoid $M$.

    Now, let us remark that the number of partitions
    in a certain equivalence class is proportional to
    the number of nanania, that is, is of the form
    $(X_i - K_i)^{n_i}$ for some $K$. We conclude that
    maximal monomials indeed have positive coefficients.
    We even conclude that
    the polynomial is in $\Nat[\vec{X}]$
    if we shift the variables with a large enough $K$. 
\end{proof}

\begin{lemma}
    \label{n-rat-correct:lem}
    The \kl{$\Nat$-rational polynomials} are in $\CorrectPoly$.
\end{lemma}
\begin{proof}[Proof Idea]
    Let $P$ be a \kl{$\Nat$-rational polynomial}.
    Let $\Sigma$  be the finite alphabet such that
    $P \in \Rel[\seqof{X_a}{a \in \Sigma}]$,
    and $f \colon \Sigma^* \to \Nat$ be the \kl{commutative}
    $\Nat$-rational series computing $P$.
    Because $f$ has polynomial growth, and is a $\Nat$-rational series,
    it is a $\Nat$-polyregular function 
    (\cref{polynomial-rational-polyreg:fact}).

    Using \cref{n-poly-combinatorics:lem},
    we conclude that maximal monomials of $P$ have
    positive coefficients. Furthermore, when fixing variables
    in $P$, we are computing a new \kl{$\Nat$-polyregular function},
    hence we also conclude that the maximal monomials have
    positive coefficients.
    We have proven that $P \in \CorrectPoly$.
\end{proof}

The core of the upcoming proof of \cref{lem:correct-to-n-rat} relies on the
following observation: if a polynomial $P$ is written $X^p + Q$, where all
terms of $Q$ have degree less than $p$, then one can find some large enough $K$
so that $X^p - (X - K)^p + Q$ also has a positive maximal coefficient.
It works because $X^p - (X - K)^p = K X^{p-1} + \cdots$, hence
the maximal coefficient can be chosen arbitrarily large by increasing
$K$.
This
trick will work similarly in multivariate polynomials, and the overall
proof scheme works as follows: for a bounded number of possible
values of $X$, we can fix the variable, and have one less item to work on.
For large enough values of $X$ (typically greater than some $K$), we can guarantee that
$X^p - (X - K)^p + Q$ has positive maximal coefficients, hence
can be computed by a $\Nat$-rational series, while
$(X - K)^p$ is clearly computable by a $\Nat$-rational series,
hence $(X^p - (X - K)^p + Q) + (X - K)^p$ is computable
as the sum of two $\Nat$-rational series, and we have
concluded that our original polynomial was a
\kl{$\Nat$-rational polynomial}. There are a number of problems in generalizing
this proof scheme:
\begin{itemize}
    \item We will have to guarantee that every polynomial considered
        is non-negative
    \item We do not only need to check that the \kl{maximal monomials}
        have \kl{positive coefficient}, but that it is the case
        when fixing arbitrarily many variables! (this
        covers the first point too)
\end{itemize}

\begin{lemma}
    Let $\vec{X}$ be a tuple of indeterminate, $Y$ be a fresh indeterminate,
    $\vec{p} \colon \vec{X}Y \to \Nat$,
    and $M \defined \times \prod_{X \in \vec{X}} X^{p(X)}$.
    Then, for all $K \geq 0$,
    $\Delta_{Y,K} \defined Y^p M - (Y - K)^p M$ has \kl{maximal monomials} with
    \kl{positive coefficients} of weight at least $K$, regardless of
    the variables fixed, as long as the (potential)
    value of $Y$ is greater
    than $K$.
\end{lemma}
\begin{proof}
    Let us first remark that
    \begin{equation*}
        \Delta_{Y,K}
        = KY^{p-1} M + Q M
        \quad .
    \end{equation*}
    In particular, there is a unique \kl{maximal monomial} for $\Delta_{Y,K}$,
    which is precisely $K Y^{p-1} M$, because all monomials
    in $Q M$ divide (strictly) $Y^{p-1} M$.
    Let us fix a variable,
    $X$ to any (non-zero) value $p > 0$. Then
    The \kl{maximal monomial} of $\restr{\Delta_{Y,K}}{X = p}$
    is exactly $\restr{KY^{p-1}M}{X = p}$, which remains
    with a \kl{positive coefficient}, that is proportional to $K$.
    Let us fix $Y$ to some value $K + l$, with $l > 0$,
    then
    $\restr{\Delta_{Y,K}}{Y = K + l}
    = (K + l)^p M - l^p M
    = ((K + l) - l) (\sum_{i = 1}^{p-1} (K + l)^i l^{p-i}) M
    = K \alpha M
    $
    which remains a monomial with a \kl{positive coefficient},
    that is proportional to $K$.
\end{proof}

@@

\begin{lemma}
    \label{lem:delta-cool}
    Let $\vec{X}$ be a tuple of indeterminate, and $Y$ be a fresh indeterminate.
    Let $P \in \Rel[\vec{X}Y]$ be in $\CorrectPoly$, and $\alpha Y^p M$ be a
    \kl{maximal monomial} of $P$, with $\alpha > 0$.
    Then, there exists a computable $K \geq 0$
    such that $\Delta_{K} \defined P - \alpha (Y - K)^p M$
    has \kl{positive coefficients} for \kl{maximal monomials}
    in any partial evaluation that satisfies $Y > K$ (if it
    gives a value to $Y$).
\end{lemma}
\begin{proof}
    Let $N$ be greater than the sum of the absolute values of all coefficients
    appearing in $P$, and let $K = 2 N$.

    Let us remark that
    \begin{equation*}
        \Delta_K = \underbrace{(P - \alpha Y^p M)}_{\text{ left hand side }}
        + \underbrace{\alpha (Y^p M - (Y - K)^p M)}_{\text{ right hand side }}
        \quad .
    \end{equation*}
    an that for every partial evaluation $\nu$ that sends $Y$ to a value
    greater than $K$,
    we have that $\restr{(Y^p M - (Y - K)^p M)}{\nu}$ has
    \kl{maximal monomials} with \kl{positive coefficients}
    proportional to $K$ (note that here ``proportional"
    implies that they are greater than $K$, because we multiply by positive
    integers).

    To conclude, it is just a game of describing how
    \kl{maximal monomials} of $\restr{\Delta_Y}{\nu}$
    can appear. If the \kl{maximal monomial} is obtained
    by summing an element of the left hand side with an element
    of the right hand side, it needs to be a \kl{maximal monomial}
    of the right hand side, and the large value of $K$ guarantees
    that the sum of coefficients is positive.
    If it only appears on the right hand side, it is even better.
    If it only appears on the left hand side, then
    in particular it means that the monomial does not
    divide $\restr{Y^p M}{\nu}$, hence has the same value
    in $\restr{\Delta_K}{\nu}$ or in $\restr{P}{\nu}$,
    which is guaranteed to be positive because $P \in \CorrectPoly$.

@@

    \textbf{Induction:}
    Assume that $\alpha Y^p M \in \MaximalMonomials(P)$
    for some indeterminate $Y$, $\alpha \neq 0$, and $p \geq 1$.
    Because $P \in \CorrectPoly$, we know that $\alpha > 0$.
    Using \cref{lem:delta-cool},
    we know that there exists a computable $K$ such that
    the polynomial
    $\Diff{K} \defined P - \alpha (Y - K)^p M$
    satisfies that for all partial valuations $\nu \colon Y\vec{X} \to \Nat$
    such that $\nu(Y) > K$ or $\nu(Y)$ is undefined,
    the \kl{maximal monomials} of $\Diff{K}$ have \kl{positive coefficients}.
    In particular, $\Diff{K}(Y - K)$  belongs to $\CorrectPoly$.
    Furthermore, $\MaximalMonomials(\Diff{K}) = \MaximalMonomials(\Diff{K}(Y - K))
    \hoarele \MaximalMonomials(P)$.
    By induction hypothesis,
    we conclude that
    $\Diff{K}(Y - K)$ is \kl{represented}
    by a \kl{star-free $\Nat$-polyregular function} $g_1$,
    \begin{equation*}
        f_1(Y, \vec{X}) \defined
        \begin{cases}
            0 & \text{ if } Y \leq K \\
            \Diff{K} & \text{ otherwise }
        \end{cases}
        \quad .
    \end{equation*}

@@

\begin{lemma}
    \label{lem:correct-covered-2}
    $\CorrectPoly[X,Y] = \CoveredPoly[X,Y]$.
\end{lemma}
\begin{proof}
    It is clear that $\CorrectPoly[X,Y] \subseteq \CoveredPoly[X,Y]$,
    by considering the empty valuation $\nu \colon \set{X,Y} \to \Nat$.
    For the converse inclusion, let us consider $P(X,Y)$
    that is \kl{non-negative}, such that the \kl{maximal monomials}
    have \kl{positive coefficients}.

>>>>

%! TeX program = xelatex
%! lang = en-US
\documentclass[sigconf,natbib=false,screen, review,anonymous]{acmart}

@@

\begin{itemize}
    \item Use $\Nat$-polyregular functions all the time, and just 
        in the introduction talk about $\Nat$-rational series.
    \item Prove that $\Nat$-rational series of polynomial 
        growth are $\Nat$-polyregular functions, maybe using
        the results about ambiguity in automata?
        Theorem 5.22
    \item Define commutativity by a map 
        $\commute \colon \Sigma^* \topartial \Nat^{\Sigma}$.
    \item Define "commutative functions" and its symbol.
    \item Define "computed by" (like, recognised by) for commutative 
        functions.
    \item Change \cref{corrected-version:thm} to use directly
        star-free!
    \item Clear up the computability problems.
    \item Polynomial + Npolyregular => star free?
    \item Polynomial + N rational => N polyregular?
    \item cite the paper of Quantitative Monadic Second-Order Logic
        about why it is interesting class.
\end{itemize}

@@

\begin{fact}[{\cite[Exercise 1.2 p 169]{berstel2011noncommutative}}]
    \label{polynomial-rational-polyreg:fact}
    Let $\Sigma$ be a finite alphabet, and $f \colon \Sigma^* \topartial \Nat$
    be a function. The following are equivalent:
    \begin{enumerate}
        \item $f$ can be computed as a \k{$\Nat$-rational series}
            of \kl{polynomial growth}.
        \item $f$ is a \kl{$\Nat$-polyregular function}.
    \end{enumerate}
\end{fact}

\begin{definition}[Letter Counting Function]
    \label{commutative-map:def}
    Let $\Sigma$ be a finite alphabet. We define
    $\commute \colon \Sigma^* \topartial \Nat^\Sigma$ for the
    map that counts occurrences of every letter in the input word, namely:
    \begin{equation*}
        \commute[w] \defined \seqof{\card[a]{w}}{a \in \Sigma} \quad .
    \end{equation*}
\end{definition}

@@

    Assume by contradiction that $P$ is a \kl{$\Nat$-rational polynomial}.
    There exists a \kl{commutative}
    $\Nat$-rational series $f \colon \Sigma \topartial \Nat$
    such that $P(\card[a]{w}, \card[b]{w}, \card[c]{w}) = f(w)$.
    Remark that $P(X,Y,Z) = 0$
    if and only if $Z(X+Y)^2 = -2 (X-Y)^2$. Hence,
    $P(X,Y,Z)=0$ if and only if $Z = 0$ and $X = Y$, or 
    $Z \neq 0$, and $X = Y = 0$.

@@

\begin{definition}
    Let $\vec{X}$ be a finite tuple of indeterminate.
    The class $\CorrectPoly[\vec{X}]$ is the collection of
    polynomials $P \in \Rel[\vec{X}]$ such that
    $P$ is 
    such that, for every partial function $\nu \colon \vec{X} \topartial \Nat$,
    every \kl{maximal monomial} of
    $\restr{P}{\nu}$ has a \kl{positive coefficient}.
\end{definition}

@@

\begin{remark}
    \label{inductive-correct-poly:remark}
    Let $P \in \Rel[X,\vec{Y}]$ be a polynomial.
    The following are equivalent:
    \begin{enumerate}
        \item $P \in \CorrectPoly$,
        \item The \kl{maximal monomials} of 
            $P$ have \kl{positive coefficients},
            and 
            for all $n \in \Nat$,
            $\restr{P}{X = n} \in \CorrectPoly$.
    \end{enumerate}
    Furthermore, if $P \in \Rel[]$ is a polynomial without
    indeterminate, then $P \in \CorrectPoly$ if and only
    if its \kl{maximal monomial} (the constant term)
    has a \kl{positive coefficient}.
\end{remark}
\begin{proof}
    By induction on the number of indeterminate,
    leveraging the fact that if there exists at least one indeterminate
    $X$, i.e., that $\vec{X} = X \vec{Y}$, then for all $n \in \Nat$
    and partial function $\nu \colon \vec{Y} \topartial \Nat$,
    we have 
    \begin{equation*}
        \restr{\left(\restr{P}{X = n}\right)}{\nu} = \restr{P}{ \nu[X = n]}
        \quad
        ,
    \end{equation*}
    where $\nu[X = n]$ is the partial function from
    $\vec{X}$ to $\Nat$ that coincides with $\nu$ on $\vec{Y}$
    and maps $X$ to $n$.
\end{proof}

\begin{example}
    \label{n-poly-n-poly:example}
    Let $P \in \Nat[\vec{X}]$. Then, $P$
    is a \kl{$\Nat$-rational polynomial}.
\end{example}
\begin{proof}
    Let $P \in \Nat[\vec{X}]$, and $\nu \colon \vec{X} \topartial \Nat$
    be a partial function.
    Notice that $\restr{P}{\nu}$ continues to be
    a polynomial with \kl{positive coefficients}, and in particular
    with 
    \kl{maximal monomials} having \kl{positive coefficients}.
\end{proof}

@@

The following \cref{n-poly-combinatorics:lem} is a slight refinement over the
classical combinatorial analysis of \kl{$\Rel$-polyregular functions}
\cite[Lemma 4.16]{LOPEZ23b} and \kl{$\Nat$-polyregular functions} that takes
into account \emph{all} \kl{maximal monomials} instead of a specific one
\cite[Lemma 5.37]{gaetanphd}.

\begin{lemma}
    \label{n-poly-combinatorics:lem}
    Let $f$ be a  \kl{$\Nat$-polyregular} function. 
    There exists $\omega \in \Nat$
    such that for all $p \in \Nat$,
    for all $\alpha_0, \dots, \alpha_p \in \Sigma^*$,
    for all $u_1, \dots, u_p \in \Sigma^*$,
    there exists a polynomial $P \in \Rel[X_1, \dots, X_p]$
    whose \kl{maximal monomials} have \kl{positive coefficients},
    and such that for all $X_1, \dots, X_p \geq \omega$:
    \begin{equation*}
        f\left(
            \alpha_0 \prod_{i = 1}^p (u_i^{\omega \times X_i} \alpha_i)
        \right)
        = P(X_1, \dots, X_p) \quad .
    \end{equation*}
\end{lemma}
\begin{proof}
    Let $\omega$ be an idempotent power for the finite monoid $M$,
    and
    $w \defined \alpha_0 \prod_{i = 1}^p (u_i^{\omega \times X_i} \alpha_i)$.
    Let $k \in \Nat$, and $\pi \colon M^k \topartial \Nat$ be such that
    $f = \pi^\dagger$. That is, 
    $f(w)$ is the sum over all factorizations of $w$
    into $k$ words $(w_1, \dots, w_k) \in \Sigma^*$
    of the value $\pi(\mu(w_1), \dots, \mu(w_k))$.

    Let us define an equivalence relation $\equiv$ over words of
    $\Sigma^*$ as follows: two words $v_1, v_2$ are equivalent if they are
    equal when normalizing them with the rules $u_i^{\omega} u_i^{\omega} \to
    u_i^{\omega}$ for all $1 \leq i \leq p$. That is, we disregard
    repetitions of the factors $u_i^{\omega}$ in the words.
    We lift the equivalence relation $\equiv$ to $k$-tuples of
    words by pointwise application.

    Remark that if $(v_1, \dots, v_k) \equiv (w_1, \dots, w_k)$ then
    $\pi(\mu(v_1), \dots, \mu(v_k)) = \pi(\mu(w_1), \dots, \mu(w_k))$ because
    $\mu(u_i^\omega) = \mu(u_i)^\omega$ is an idempotent element of the monoid
    $M$. In particular, $f(w)$ can be computed as the sum over equivalence
    classes for $\equiv$, of the value of $\pi$ on one representative,
    which belongs to $\Nat$.

    Therefore, it suffices to prove that the number of partitions of $w$ in a
    single equivalence class for $\equiv$ is a polynomial $P(X_1, \dots, X_p)$
    with \kl{positive coefficients} for its \kl{maximal monomials}.

    Notice that to produce all elements in a given equivalence class
    means adding the factors $u_i^\omega$ where $1 \leq i \leq p$
    back to the normalized version
    of the equivalence class. For all elements in an equivalence class,
    one has to add the same amount of $u_i^\omega$ for $1 \leq i \leq p$,
    and therefore the number of possible choices
    is either constant, or 
    is a product of binomials of the form $\binom{X - l}{s}$
    which has the desired shape.
\end{proof}

\begin{lemma}
    \label{n-rat-correct:lem}
    Let $P \in \Rel[X_1, \dots, X_p]$ be \kl{represented}
    by a \kl{$\Nat$-rational series}. Then,
    $P \in \CorrectPoly$.
\end{lemma}
\begin{proof}
    Let $f$ be the \kl{commutative}
    \kl{$\Nat$-rational series}
    with domain $\Sigma \defined \set{a_1, \dots, a_p}$
    that \kl{represents} $P$. Because $f$ has \kl{polynomial growth},
    it is in fact a \kl{$\Nat$-polyregular function}
    (\cref{polynomial-rational-polyreg:fact}).
    Using \cref{n-poly-combinatorics:lem},
    there exists a number $\omega \in \Nat$
    and polynomial $Q$ with \kl{positive coefficients} for its
    \kl{maximal monomials} such that
    for all $X_1, \dots, X_p \geq \omega$:
    \begin{equation*}
        f\left(
            \prod_{i = 1}^p (a_i)^{\omega \times X_i}
        \right)
        = Q(X_1, \dots, X_p)
        = P(\omega X_1, \dots, \omega X_p) 
        \quad .
    \end{equation*}
    We conclude that $P(\omega X_1, \dots, \omega X_p) = Q(X_1, \dots, X_p)$
    as polynomials,
    and in particular that
    the \kl{maximal monomials} of 
    $P$ have \kl{positive coefficients}.

    Remark that for every partial valuation $\nu \colon \vec{X} \topartial \Nat$,
    the polynomial $\restr{P}{\nu}$ continues to be represented
    by a \kl{$\Nat$-polyregular function}, namely
    $f$ partially applied to a word. As a consequence,
    the \kl{maximal monomials} of
    $\restr{P}{\nu}$ also have \kl{positive coefficients}, and 
    we have proven that $P \in \CorrectPoly$.
\end{proof}

\textbf{TODO: rewrite this}
The core of the upcoming proof of \cref{lem:correct-to-n-rat} relies on the
following observation: if a polynomial $P$ is written $X^p + Q$, where all
terms of $Q$ have \kl{degree} less than $p$, then one can find some large
enough $K \in \Nat$ so that $X^p - (X - K)^p + Q$ also has a positive maximal
coefficient. It works because $X^p - (X - K)^p = K X^{p-1} + \cdots$, hence the
new \kl{maximal monomial} can be made to have arbitrarily large \kl{coefficient}
by increasing $K$.
As a consequence, for values $n \leq K$ of $X$, one can compute $\restr{P}{X =
n}$ which remains in $\CorrectPoly$, and apply an induction hypothesis.
Furthermore, for values $n > K$ of $X$, one has the guarantee that $X^p - (X -
K)^p + Q$ has positive maximal coefficients, hence can be computed by a
$\Nat$-rational series, while $(X - K)^p$ is clearly computable by a
$\Nat$-rational series, hence $(X^p - (X - K)^p + Q) + (X - K)^p$ is computable
as the sum of two $\Nat$-rational series, and we have concluded that our
original polynomial was a \kl{$\Nat$-rational polynomial}.

When multiple indeterminate are involved, a bit of care is needed, and
this is the technical content of \cref{diff-one-monomial:lem,lem:delta-cool}.

\begin{definition}
    Let $\vec{X}$ be a tuple of indeterminate, let $Y$
    be a fresh indeterminate,
    and 
    let $P \in \Rel[\vec{X},Y]$ be a polynomial.
    For every \kl{maximal monomial}
    $\alpha Y^p M$ of $P$ such that $M \in \Rel[\vec{X}]$, and every $K \in \Nat$,
    we define
    \begin{equation*}
        \Diff{K}{\alpha Y^p M}{P} \defined 
        P - \alpha (Y - K)^p M \quad .
    \end{equation*}
\end{definition}

\begin{lemma}
    \label{diff-one-monomial:lem}
    Let $\vec{X}$ be a tuple of indeterminate, $Y$ be a fresh indeterminate,
    and $P = Y^p M$ where $M$ is a \kl{monomial} over $\vec{X}$.
    Then, for all $K \geq 0$,
    for all $\nu \colon \vec{X}Y \topartial \Nat$
    such that $\nu(Y) > K$ or $\nu(Y)$ is undefined,
    $\restr{\Diff{K}{Y^pM}{Y^pM}}{\nu}$
    has \kl{maximal monomials} with
    coefficients at least $K$, or is the constant polynomial equal to zero.
\end{lemma}
\begin{proof}
    Let us write $\Delta_K$ as a shorthand for
    $\Diff{K}{Y^p M}{Y^p M}$.
    Let us first remark that
    there exists $Q \in \Rel[Y]$ of degree at most $p-2$
    such that:
    \begin{equation*}
        \Delta_K
        = KY^{p-1} M + Q M
        \quad .
    \end{equation*}
    In particular, there is a unique \kl{maximal monomial} for $\Delta_{K}$,
    which is precisely $K Y^{p-1} M$, because all monomials
    in $Q M$ \kl{strictly divide} $Y^{p-1} M$.

    Let $\nu \colon \vec{X}Y \topartial \Nat$ be a partial valuation such that
    $\restr{\Delta_K}{\nu} \neq 0$. If $\nu(Y)$ is undefined, then the
    \kl{maximal monomial} of $\restr{\Delta_K}{\nu}$ is exactly $K Y^{p-1}
    \restr{M}{\nu}$, and $\restr{M}{\nu} \neq 0$. Therefore, the unique
    \kl{maximal monomial} of $\restr{\Delta_K}{\nu}$ has a \kl{positive
    coefficient} that is at least $K$.

    Otherwise, if $\nu(Y) > K$, then $\nu(Y) = K + l$ for some $l \in \Nat$.
    Let us write $\mu$ for the restriction of $\nu$ to indeterminates of $\vec{X}$.
    We can compute 
    \begin{align*}
        \restr{\Delta_K}{\nu}
        &= (K + l)^p \restr{M}{\mu} - l^p \restr{M}{\mu}\\
        &= ((K + l)^p - l^p) \restr{M}{\mu} \\
        &= (K + l - l)\left(\sum_{i = 0}^{p-1} (K+l)^i l^{p-i}\right) 
        \restr{M}{\mu} \\
        &= K \alpha \restr{M}{\mu} 
        \quad .
    \end{align*}
    Which proves that the \kl{maximal monomial} of
    $\restr{\Delta_K}{\nu}$ has a coefficient
    that is at least $K$.
\end{proof}

@@

\begin{lemma}
    \label{lem:delta-cool}
    Let $\vec{X}$ be a tuple of indeterminate, and $Y$ be a fresh indeterminate.
    Let $P \in \Rel[\vec{X}Y]$ be in $\CorrectPoly$, and $\alpha Y^p M$ be a
    \kl{maximal monomial} of $P$, with $\alpha > 0$.
    Then, there exists a computable $K \geq 0$
    such that
    for all $\nu \colon \vec{X}Y \topartial \Nat$
    such that $\nu(Y) > K$ or $\nu(Y)$ is undefined,
    the \kl{maximal monomials} of 
    $\restr{\Diff{K}{Y^pM}{P}}{\nu}$
    have \kl{positive coefficients}.
\end{lemma}
\begin{proof}
    Let $N$ be greater than the sum of the absolute values of all coefficients
    appearing in $P$, and let $K \defined N + 1$.
    Let us write $\Delta_K$
    as a shorthand for
    $\Diff{K}{\alpha Y^p M}{P}$, and decompose $\Delta_K$ as follows:
    \begin{equation*}
        \Delta_K
        = \underbrace{(P - \alpha Y^p M)}_{Q_1}
        + \underbrace{\alpha (Y^p M - (Y - K)^p M)}_{Q_2}
        \quad .
    \end{equation*}

    Applying \cref{diff-one-monomial:lem}, we know that for every partial
    evaluation $\nu \colon \vec{X}Y \topartial \Nat$ such that $\nu(Y) > K$ or
    $\nu(Y)$ is undefined, the \kl{maximal monomials} of $\restr{Q_2}{\nu}$
    have \kl{positive coefficients}, and that these coefficients are either $0$
    (the polynomial is constant equal to zero) or at least $K$.

    To conclude, it is just a matter of describing how \kl{maximal monomials}
    of $\restr{\Delta_K}{\nu}$ can appear. Let us proceed by case analysis. If
    $\restr{Q_2}{\nu} = 0$, then, $\restr{\alpha Y^p M}{\nu} = 0$, and
    $\restr{\Delta_K}{\nu} = \restr{P}{\nu}$, in which case we conclude because
    $P \in \CorrectPoly$. Otherwise, we know that $\restr{Q_2}{\nu} \neq 0$,
    and that its (unique) \kl{maximal monomial} has a \kl{positive coefficient}
    that is at least $K$.
    Let us now consider a \kl{maximal monomial} $M_0$
    of $\restr{P}{\nu}$. This \kl{monomial} is obtained
    by summing \kl{monomials} from $\restr{Q_1}{\nu}$ and $\restr{Q_2}{\nu}$.
    Note that, by construction

    Because $\alpha Y^p M$ is a \kl{maximal monomial} of
    $P$, and since $K$ is greater than the sum of
    the absolute values of all coefficients appearing in $P$,
    we conclude that

    If a \kl{maximal monomial} of $\restr{\Delta_K}{\nu}$
    is obtained
    by summing a of $\restr{Q_1}{\nu}$
    by summing an element of the left hand side with an element
    of the right hand side, it needs to be a \kl{maximal monomial}
    of the right hand side, and the large value of $K$ guarantees
    that the sum of coefficients is positive.
    If it only appears on the right hand side, it is even better.
    If it only appears on the left hand side, then
    in particular it means that the monomial does not
    divide $\restr{Y^p M}{\nu}$, hence has the same value
    in $\restr{\Delta_K}{\nu}$ or in $\restr{P}{\nu}$,
    which is guaranteed to be positive because $P \in \CorrectPoly$.

@@

    \textbf{Induction:}
    Assume that $\alpha Y^p M \in \MaximalMonomials(P)$
    for some indeterminate $Y$, $\alpha \neq 0$, and $p \geq 1$.
    Because $P \in \CorrectPoly$, we know that $\alpha > 0$.
    Using \cref{lem:delta-cool},
    we know that there exists a computable $K$ such that
    the polynomial
    $\Diff{K} \defined P - \alpha (Y - K)^p M$
    satisfies that for all partial valuations $\nu \colon Y\vec{X} \topartial \Nat$
    such that $\nu(Y) > K$ or $\nu(Y)$ is undefined,
    the \kl{maximal monomials} of $\Diff{K}$ have \kl{positive coefficients}.
    In particular, $\Diff{K}(Y - K)$  belongs to $\CorrectPoly$.
    Furthermore, $\MaximalMonomials(\Diff{K}) = \MaximalMonomials(\Diff{K}(Y - K))
    \hoarele \MaximalMonomials(P)$.
    By induction hypothesis,
    we conclude that
    $\Diff{K}(Y - K)$ is \kl{represented}
    by a \kl{star-free $\Nat$-polyregular function} $g_1$,
    \begin{equation*}
        f_1(Y, \vec{X}) \defined
        \begin{cases}
            0 & \text{ if } Y \leq K \\
            \Diff{K} & \text{ otherwise }
        \end{cases}
        \quad .
    \end{equation*}

@@

\begin{lemma}
    \label{lem:correct-covered-2}
    $\CorrectPoly[X,Y] = \CoveredPoly[X,Y]$.
\end{lemma}
\begin{proof}
    It is clear that $\CorrectPoly[X,Y] \subseteq \CoveredPoly[X,Y]$,
    by considering the empty valuation $\nu \colon \set{X,Y} \topartial \Nat$.
    For the converse inclusion, let us consider $P(X,Y)$
    that is \kl{non-negative}, such that the \kl{maximal monomials}
    have \kl{positive coefficients}.
